Performance of Rookie Can Predict Price of Their Rookie Prizm Silver Cards

### 2024-04-24 paper/paper.qmd
compiled results

test_maxey_price_only <- clean_maxey[, -1]

@@

test_haliburton_price_only <- clean_haliburton[, -1]

@@

test_anthony_price_only <- clean_anthony_edward[, -1]

@@

## Price of increasing performance

>>>>

test_maxey_price_only <- maxey[, -1]

@@

test_haliburton_price_only <- haliburton[, -1]

@@

test_anthony_price_only <- anthony_edward[, -1]

@@

## Tyrese Maxey Preduction
```{r}
#| label: fig-1
#| fig-cap: The comparision between past season versus predicted improving season
#| fig-subcap: ["Amount of Power Plays", "Effectiveness of Power Plays"]
#| echo: false
#| warning: false
#| layout-ncol: 2

library(ggplot2)

maxey_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
  geom_line(group =1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Predicted price of future seasons with improving performance",
    x = "Dates",
    y = "Price"

  )+ 
  geom_point() +
  geom_smooth(method=lm)

price_data |> ggplot(aes(x = `Date`, y = `Tyrese Maxey`)) + 
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Predicted price of future seasons with improving performance",
    x = "Dates",
    y = "Price"

  )

## Tyrese Haliburton Preduction
```{r}
#| label: fig-2
#| fig-cap: The comparision between past season versus predicted improving season
#| fig-subcap: ["Amount of Power Plays", "Effectiveness of Power Plays"]
#| echo: false
#| warning: false
#| layout-ncol: 2

library(ggplot2)

haliburton_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
  geom_line(group =1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Predicted price of future seasons with improving performance",
    x = "Dates",
    y = "Price"

  )+ 
  geom_point() +
  geom_smooth(method=lm)

price_data |> ggplot(aes(x = `Date`, y = `Tyrese Haliburton`)) + 
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Predicted price of future seasons with improving performance",
    x = "Dates",
    y = "Price"

  )

## Anthony Edward Prediction

```{r}
#| label: fig-3
#| fig-cap: The comparision between past season versus predicted improving season
#| fig-subcap: ["Amount of Power Plays", "Effectiveness of Power Plays"]
#| echo: false
#| warning: false
#| layout-ncol: 2

library(ggplot2)

anthony_prediction_table |> ggplot(aes(x = `Month`, y = `Predicted Price`)) + 
  geom_line(group =1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Predicted price of future seasons with improving performance",
    x = "Dates",
    y = "Price"

  )+ 
  geom_point() +
  geom_smooth(method=lm)

price_data |> ggplot(aes(x = `Date`, y = `Anthony Edward`)) + 
  geom_line(group = 1) +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.9, hjust=1)) +
  labs(
    title = "Predicted price of future seasons with improving performance",
    x = "Dates",
    y = "Price"

  )
